---
#title: "Weather Report "
output:
  officedown::rdocx_document:
    reference_docx: template.docx
always_allow_html: false
params:
  site_selection: !r c("Abbotsinch", "Heathrow","Marham","Waddington")
  domain: localhost
---

```{r load_data, message=TRUE, warning=FALSE, include=FALSE, paged.print=FALSE}
library("tidyverse")
source("functions.R")

# load additional packages for Word file
packages <- c("officedown",    # Additional word functionality
              "officer",
              "stringi")       # string manipulation

loaded_packages <- paste0(search(),sep=" ",collapse = "")
packages <- tibble(package = packages)
packages <- packages %>% mutate(loaded=str_detect(loaded_packages, package, negate = FALSE)) %>% pull(package)

if(length(packages)>0 ){
    for(i in 1:length(packages)){
        result <- require(packages[i],character.only = TRUE)
        if(!result){
            install.packages(packages[i])
            library(packages[i],character.only = TRUE)
        }
    }
}

#don't show code, set image resolution
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE,
                      dpi = 300, dev.args = list(bg = 'transparent'))



#load data 
sites <- read_csv("Data/Sites.csv")


sites <- sites %>% filter(Site_Name %in% params$site_selection)
station_data<- data_loader(sites)
processed_data <- aggregate_data(station_data)


#extract site names for list of sites

site_names <- paste(params$site_selection,collapse = ", ")
site_names <- stri_replace_last_fixed(site_names,",",", and")    # Oxford comma!!!




#plot dimensionsa
column_witdh <- 3.25                        ### set up manually
column_height <- (1199/1500)*column_witdh   ### ration set up after checking png output (not exepcted to change, so set manually)

#set different sizes for charts's labels if app is running on shinyapps.io

if(grepl( "127.0.0.1", params$domain, fixed = TRUE)){
        s1 <-16
        s2 <-10
        message(1)
}else{
      s1 <-32
      s2 <-24
      message(2)
}

```
\

`r external_img(src = "www/day-cloud-snow.png", height = 1.5, width = 1.5)` \
`r ftext(paste("Weather Report for",site_names), fp_text(color = "navy", font.size = 50, bold = TRUE, font.family = "Roboto"))` `r fp_par(text.align = "center", padding.top = 30)`

`r run_pagebreak()`

# Disclaimer
\

This report has been created as an assignment for **STATS5078 - R Programming**, part of the MSc in Data Analytics (ODL) programme at the University of Glasgow.
\

The content of this file is only displayed for illustrative purposes. The author is not responsible for data accuracy.
\

Generated on server *`r params$domain`*.

`r run_pagebreak()`


# Seven Day Summary
\

```{r seven_day_table}

seven_day_datatable(processed_data)
```
`r run_pagebreak()`

# Air Temperature

\

```{r temp_charts}
block_section(
  prop_section(
    type = "continuous"
  )
)

p_temp_mean <- plot_data(processed_data,"monthly","mean","air_temperature","Date",size1=s1,size2=s2) 
p_temp_max <- plot_data(processed_data,"daily","max","air_temperature","Date",size1=s1,size2=s2) 
p_temp_min <-plot_data(processed_data,"daily","min","air_temperature","Date",size1=s1,size2=s2) 

if(!dir.exists("png")) dir.create("png")
ggsave("png/p_temp_mean.png",p_temp_mean)
ggsave("png/p_temp_max.png",p_temp_max)
ggsave("png/p_temp_min.png",p_temp_min)

```


`r external_img(src = "png/p_temp_mean.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_temp_min.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_temp_max.png", height = column_height, width = column_witdh)`


```{r section_temp}
block_section(
  prop_section(
    type = "continuous",
    section_columns =
      section_columns(
        widths = rep(column_witdh, 3 ), space = 0.05, sep = FALSE
      )
  )
)
```

`r run_pagebreak()`

# Relative Humidity
\

```{r hum_charts}
block_section(
  prop_section(
    type = "continuous"
  )
)

p_hum_mean <- plot_data(processed_data,"monthly","mean","rltv_hum","Date",size1=s1,size2=s2) 
p_hum_max <- plot_data(processed_data,"daily","max","rltv_hum","Date",size1=s1,size2=s2) 
p_hum_min <-plot_data(processed_data,"daily","min","rltv_hum","Date",size1=s1,size2=s2) 

if(!dir.exists("png")) dir.create("png")
ggsave("png/p_hum_mean.png",p_hum_mean)
ggsave("png/p_hum_max.png",p_hum_max)
ggsave("png/p_hum_min.png",p_hum_min)

```


`r external_img(src = "png/p_hum_mean.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_hum_min.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_hum_max.png", height = column_height, width = column_witdh)`


```{r section_hum}
block_section(
  prop_section(
    type = "continuous",
    section_columns =
      section_columns(
        widths = rep(column_witdh, 3 ), space = 0.05, sep = FALSE
      )
  )
)
```

`r run_pagebreak()`

# Wind Speed

\

```{r wind_charts}
block_section(
  prop_section(
    type = "continuous"
  )
)

p_wind_mean <- plot_data(processed_data,"monthly","mean","wind_speed","Date",size1=s1,size2=s2) 
p_wind_max <- plot_data(processed_data,"daily","max","wind_speed","Date",size1=s1,size2=s2) 
p_wind_min <-plot_data(processed_data,"daily","min","wind_speed","Date",size1=s1,size2=s2) 

if(!dir.exists("png")) dir.create("png")
ggsave("png/p_wind_mean.png",p_wind_mean)
ggsave("png/p_wind_max.png",p_wind_max)
ggsave("png/p_wind_min.png",p_wind_min)

```


`r external_img(src = "png/p_wind_mean.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_wind_min.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_wind_max.png", height = column_height, width = column_witdh)`


```{r section_wind}
block_section(
  prop_section(
    type = "continuous",
    section_columns =
      section_columns(
        widths = rep(column_witdh, 3 ), space = 0.05, sep = FALSE
      )
  )
)
```

`r run_pagebreak()`

# Visibility
\

```{r visib_charts}
block_section(
  prop_section(
    type = "continuous"
  )
)

p_visib_mean <- plot_data(processed_data,"monthly","mean","visibility","Date",size1=s1,size2=s2) 
p_visib_max <- plot_data(processed_data,"daily","max","visibility","Date",size1=s1,size2=s2) 
p_visib_min <-plot_data(processed_data,"daily","min","visibility","Date",size1=s1,size2=s2) 

if(!dir.exists("png")) dir.create("png")
ggsave("png/p_visib_mean.png",p_visib_mean)
ggsave("png/p_visib_max.png",p_visib_max)
ggsave("png/p_visib_min.png",p_visib_min)

```


`r external_img(src = "png/p_visib_mean.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_visib_min.png", height = column_height, width = column_witdh)`
`r run_columnbreak()`
`r external_img(src = "png/p_visib_max.png", height = column_height, width = column_witdh)`


```{r section_visib}
block_section(
  prop_section(
    type = "continuous",
    section_columns =
      section_columns(
        widths = rep(column_witdh, 3 ), space = 0.05, sep = FALSE
      )
  )
)
```
